---
html_document:
  code_folding: hide
author: "Thomas Gredig"
fig_width: 8
output:
  html_document:
    df_print: paged
  pdf_document: null
  toc: yes
title: 'Kaggle: World University Ranking Data Set'
number_sections: no
highlight: tango
theme: cosmo
fig_height: 6
toc: yes
---

```{r libraries_and_packages_management,message=FALSE,warning=FALSE}
#use pacman for package management
if (!require("pacman")) install.packages("pacman")
pacman::p_load(knitr, kableExtra, formattable, dplyr, tm, tidyr, wordcloud, httr,
               ggplot2, treemap, gridExtra, grid, fmsb, leaflet, plotly,reshape, corrplot,ggrepel)

options(knitr.table.format = "html") 
```

# Data Loading

Let's get the data

```{r}
source('load-data.R')
```

# Display Data {.tabset .tabset-fade .tabset-pills}

We have 6 data files in University Rankings dataset, as following:

* cwurData.csv (`r nrow(cwurData)` rows, `r length(names(cwurData))` columns)  
* education_expenditure_supplementary_data.csv (`r nrow(educationExpenditure)` rows, `r length(names(educationExpenditure))` columns)  
* educational_attainment_supplementary_data.csv (`r nrow(educationalAttainment)` rows, `r length(names(educationalAttainment))` columns)  
* school_and_country_table.csv (`r nrow(schoolCountry)` rows, `r length(names(schoolCountry))` columns)  
* shanghaiData.csv (`r nrow(shanghaiData)` rows, `r length(names(shanghaiData))` columns)  
* timesData.csv (`r nrow(timesData)` rows, `r length(names(timesData))` columns)  



## CWUR
```{r glimpse_cwurData}
#knitr::kable(head(cwurData,10),caption="Center World University Rankings information (first 10 rows)")
kable(head(cwurData,10), "html") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
glimpse(cwurData)
```

## Shanghai
```{r glimpse_shanghaiData}
knitr::kable(head(shanghaiData,10),caption="Shanghai Ranking information (first 10 rows)")
glimpse(shanghaiData)
```

## Times
```{r glimpse_timesData}
knitr::kable(head(timesData,10),caption="Times Higher Education World University Rankings data information (first 10 rows)")
glimpse(timesData)
```

## Education expenditure
```{r glimpse_educationExpenditure}
knitr::kable(head(educationExpenditure,10),caption="Education expenditure information (first 10 rows)")
glimpse(educationExpenditure)
```

## Education attainment
```{r glimpse_educationalAttainment}
knitr::kable(head(educationalAttainment,10),caption="Education attainment information (first 10 rows)")
glimpse(educationalAttainment)
```

## School & country
```{r glimpse_schoolCountry}
knitr::kable(head(schoolCountry,10),caption="School & country information (first 10 rows)")
glimpse(schoolCountry)
```


# Analysis

```{r}

```